\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fontenc}
\usepackage{tgpagella} % pleasant serif; change if not available
\renewcommand{\familydefault}{\rmdefault}

% Compact section headings
\titleformat{\section}{\large\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{6pt}{6pt}

% Small helper commands
\newcommand{\header}[1]{\begin{center}\LARGE\scshape #1\end{center}}
\newcommand{\contact}[1]{\begin{center}{\small #1}\end{center}}
\newcommand{\subheading}[2]{\noindent\textbf{#1} \hfill {\small #2}\par}
\newcommand{\itembullet}[1]{\item #1}

\begin{document}

\header{Nishant Dwivedi}
\contact{\href{mailto:idwivedi1204@gmail.com}{idwivedi1204@gmail.com} \; | \; +91-9125007419 \; | \; \href{https://www.linkedin.com/in/nishant1205/}{LinkedIn} \; | \; \href{https://github.com/nishant4500}{GitHub} \; | \; \href{https://leetcode.com/u/idwivedi1204/}{LeetCode}}

\section*{Education}
\subheading{Jaypee Institute of Information Technology, Noida}{Sept 2022 -- May 2026}
B.Tech., Electronics and Communication Engineering \hfill CGPA: 7.7/10

\vspace{4pt}
\subheading{Kendriya Vidyalaya, Raebareli}{July 2021 -- July 2022}
Class XII \hfill Percentage: 92.6\%

\vspace{4pt}
\subheading{Kendriya Vidyalaya, Raebareli}{July 2019 -- July 2020}
Class X \hfill Percentage: 91.2\%

\section*{Experience}
\subheading{Research Intern -- Indian Institute of Technology (IIT) BHU}{May 2025 -- July 2025}
\begin{itemize}[left=*,noitemsep,nolistsep]
  \item Worked on design and simulation of a low-profile, electronically beam-steerable flat-lens antenna using Huygens' metasurface principles (Ka-band).
  \item Modeled unit-cells, implemented bias control using varactor diodes, and developed MATLAB/Python phase programming for 3D beam steering.
  \item Simulated and optimized radiation patterns; visualized results with MATLAB and Python scripts.
\end{itemize}

\vspace{6pt}
\subheading{Full-Stack E-Commerce Platform -- Codectechnologies}{July 2025 -- August 2025}
\begin{itemize}[left=*,noitemsep,nolistsep]
  \item Built a MERN-stack e-commerce web application with JWT-based authentication and Stripe-powered checkout.
  \item Implemented product listing, search/filter, cart management, and an admin dashboard with role-based access control.
\end{itemize}

\section*{Projects}
\subheading{Transgender Support Web Platform}{June 2024 -- July 2024}
\begin{itemize}[left=*,noitemsep,nolistsep]
  \item Enhanced a MERN full-stack application addressing discrimination, employment, and housing access challenges.
  \item Implemented a real-time supportive chatbot (Node.js + WebSockets) for confidential guidance.
  \item Built a Job Opportunities Hub and Safe Spaces Locator using REST APIs and MongoDB geospatial queries.
  \item Added a moderated Blogs feature for community knowledge sharing; deployed frontend on Netlify and backend on Render with MongoDB.
\end{itemize}

\vspace{6pt}
\subheading{Real-Time Chat \& Server Monitoring Application (Backend)}{Mar 2023 -- Sep 2023}
\begin{itemize}[left=*,noitemsep,nolistsep]
  \item Implemented a full-stack real-time chat app with Node.js backend supporting many concurrent users.
  \item Built a real-time server monitoring dashboard showing CPU/memory metrics using Node.js (Cluster, WebSockets) and MongoDB.
  \item Deployed to Heroku, maintaining high availability for chat and monitoring services.
\end{itemize}

\section*{Technical Skills}
C++, SQL, MATLAB, Python, JavaScript, React.js, Node.js, HTML, CSS, Excel

\section*{Achievements}
\begin{itemize}[left=*,noitemsep,nolistsep]
  \item Solved 300+ competitive programming problems on LeetCode and CodeChef using C++.
  \item Published IEEE International Conference paper (ISPCC) on topic: Solar Cell.
  \item 1st Position in IEEE Contest: \href{https://certificatlink.com/}{Link}
  \item Top 5 in Round 2 of RIDEHACK 2024 (CICE Hub JIIT): \href{https://drive.google.com/file/d/1dG66lAQD9de7Z82KSTbs3FbJTwxANfKZ/view?usp=sharing}{Link}
\end{itemize}

\end{document}
